
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\chapter*{ACKNOWLEDGMENTS}

\setstretch{1.5}

\tab This dissertation would not have been possible without the assistance of many people. I apologize in advance if I inadvertently forget to mention anyone.

I would like to begin by thanking my advisor, Professor Jim Freudenberg. Jim was the perfect advisor for me, i.e., most of the time he left me alone so that I could get work done, but he was always available when I needed his guidance. I am really going miss stopping by his office for our late night chats.

I would like to especially thank my dissertation committee: Professors Jessy Grizzle,Pramod Khargonekar, Fred Terry, and Dr. Michael Elta. I could not have asked for a better group of individuals to guide me over the years. They have been great teachers, both inside and outside of the class room, and great friends. I would also like to thank Dr. Martin Giles for his guidance in developing models and simulations for the etching process.

There are a number of people without whose help this research would not have been possible. I would like to thank Keith, Jim and Terry for all their assistance in wafer processing and equipment maintenance. I would especially like to thank Jeff for serving unofficially as my cleanroom mentor. Jeff has taught me most of what I know about running and maintaining semiconductor processing equipment. His guidance has been as valuable to me as that of my dissertation committee. I would also like to thank Don, Chuck, Hugh, Laura, Liz, and Jon for all they have done in maintaining the computers that I have relied on during this research.

I have been very lucky to have the opportunity to work with a group of talented students during my years at the University of Michigan. I want to thank Courtney, Tyrone B., Tyrone V., Pete H., Pete K., Oliver, Anna, Meera, Manish, Steve T., Bill and A1 for being great friends and research partners over the past few years. A special thanks to everyone who helped to proof read this dissertation. Your comments and suggestions have been invaluable. I wish you all the best of luck as you finish up your graduate studies.

One person who has made my last year here very special has been Steve R. I have really enjoyed teaching Steve many of the research skills that I have learned over the years. It makes it easier to leave knowing that I am leaving the Mule in such capable hands. I wish Steve all the best in continuing this research where I have left off.

I would like to thank the Semiconductor Research Corporation (SRC), the DeVlieg Foundation and the National Aeronautics and Space Administration (NASA) for the financial support that made my graduate education possible.

I would have not made it though 22 years of school without the love and support of my family. My mother and father have done so much for me, I wouldn’t know where to begin to thank them. I love you both more than anything. Thanks for everything. I would also like to thank by brother whose love and support has always meant a lot to me. In addition, I would like to thank Mom and Dad O’Rourke for providing me with the love and support of a second family. And I can’t begin to thank my wife, Krista, for everything that she has done for me. Her love and friendship have kept me going through the hardest of times.

The one person that I am going to miss most in leaving Michigan is Jon Friedman. Jon has been my best friend and so much more over the past 5 years. Michigan would just not have been the same without him.

\clearpage
