 \addcontentsline{toc}{chapter}{Bibliography}
 
 \begin{thebibliography}{100}% 100 is a random guess of the total number of
	%references
	
	\addtolength{\leftmargin}{0.2in} % sets up alignment with the following line.
	\setlength{\itemindent}{-0.2in}
	
	\bibitem{A.C. Adams and C.D. Capio} A.C. Adams and C.D. Capio. Edge profiles in the plasma etching of polycrystalline silicon. \emph{Journal of the Electrochemical Society}, 128(2):366-370, February 1981.
	
	\bibitem{K.D. Allen and H.H. Sawin} K.D. Allen and H.H. Sawin. The plasma etching of polysilicon with $\text{CF}_{3}\text{Cl}/\text{Ar}$ discharges. II. Modeling of ion bombardment energy distributions. \emph{Journal of the Electrochemical Society}, 133(ll):2326-2338, November 1986.

	
	\bibitem{K.D. Allen, H.H. Sawin, M.T. Mocella, and M,W. Jenkins} K.D. Allen, H.H. Sawin, M.T. Mocella, and M,W. Jenkins. The plasma etching of polysilicon with $\text{CF}_{3}\text{Cl}/\text{Ar}$ discharges. I. Parametric modeling and impedance analysis. \emph{Journal of the Electrochemical Society}, 133(ll):2315-2325, November 1986.
	
	\bibitem{B.D.O. Anderson and J.B. Moore} B.D.O. Anderson and J.B. Moore. \emph{Optimal Control: Linear Quadratic Methods}. Prentice Hall, 1990.
	
	\bibitem{J.C Arnold} J.C. Arnold. \emph{Material Transport and Reaction Effects on Surface Topography Evolution During Plasma Etching}. Ph.D. Dissertation, Massachusetts Institute of Technology, 1994.
	
	\bibitem{K.J. Astrom and B. Wittenmark.} K.J. Astrom and B. Wittenmark. \emph{Computer-Controlled Systems: Theory and Design.} Prentice Hall, 1990.

	\bibitem{D.M. Auslander and C.H. Tham} D.M. Auslander and C.H. Tham. \emph{Real Time Software fo r Control: Program Examples in C}. Prentice-Hall, 1990.
	
	\bibitem{A.J. Bariya, C.W. Frank, and J.P. McVittie} A.J. Bariya, C.W. Frank, and J.P. McVittie. A surface kinetic model for plasma polymerization with application to plasma etching. \emph{Journal of the Electrochemical Society}, 137(8):2575-2581, August 1990.
	
	\bibitem{T.E. Benson, P.D. Hanish C.K. Hanish} T.E. Benson, P.D. Hanish C.K. Hanish, L.I. Kamlet, P. Klimecky, B.A. Rashap, S.M. Ruegsegger, J.S. Freudenberg, J.W. Grizzle, P.P. Khargonekar, F.L. Terry, Jr., and B. Barney. Sensor systems for real-time feedback control of reactive ion etching. \emph{In Proceedings of the NCCAVS Advanced Plasma Tools Workshop}, 1995.
	
	\bibitem{G.E.P. Box and N.R. Draper} G.E.P. Box and N.R. Draper. \emph{Empirical Model-Building and Response Surfaces}. John Wiley \& Sons, 1987.
	
	\bibitem{T. Breedijk} T. Breedijk. \emph{Model Identification and Nonlinear Predictive Control of Rapid Thermal Processing Systems}. Ph.D. Dissertation, University of Texas at Austin, 1994.
	
	\bibitem{S.W. Butler} S.W. Butler. \emph{Etching and Polymerization in Fluorocarbon-Hydrogen Plasma: Mathematical Modeling and Experimental Investigation}. Ph.D. Dissertation, University of Texas at Austin, 1991.
	
	\bibitem{S.W. Butler, K.J. McLaughlin} S.W. Butler, K.J. McLaughlin, T.F. Edgar, and I. Trachtenberg. Development of techniques for real-time monitoring and control in plasma etching: II. Multivariable control system analysis of manipulated, measured, and performance variables. \emph{Journal of the Electrochemical Society}, 138(9):2727-2735, September 1991.
	
	\bibitem{E.G. Celii, T.-C. Kao, A.J. Katz} E.G. Celii, T.-C. Kao, A.J. Katz, T.S. Moise, M. Woolsey, and B. Jobs. EUipsometrybased control for III-V MBE growth. \emph{In Extended Abstracts: 187th Meeting of the Electrochemical Society}, pages 203-204, May 1995.
	
	\bibitem{M. Chandhok, P.D. Hanish} M. Chandhok, P.D. Hanish, and J.W. Grizzle. Phenomenological modehng for real-time control of RIE. \emph{In Extended Abstracts: 187th Meeting of the Electrochemical Society}, pages 162-164, May 1995.
	
	\bibitem{B. Chapman} B. Chapman. \emph{Glow Discharge Processes: Sputtering and Plasma Etching}. John Wiley \& Sons, 1980.
	
	\bibitem{C.T. Chen} C.T. Chen. \emph{Linear Systems Theory and Design}. Harcourt Brace Jovanovich, 1984.
	
	\bibitem{X. Cheng, T.J. Knight} X. Cheng, T.J. Knight, B.H. Krogh, D.W. Greve, and M.A. Gibson. Application of sampling quadrupole mass spectrometry to multivariable process control. \emph{In Extended Abstracts: 187th Meeting of the Electrochemical Society}, pages 201-202, May 1995.
	
	\bibitem{Y.M. Cho and T. Kailath} Y.M. Cho and T. Kailath. Model identification in rapid thermal processing systems. \emph{IEEE Transactions on Semiconductor Manufacturing}, 6(3):233-245, August 1993.
	
	\bibitem{J.W. Coburn} J.W. Coburn. Role of ions in reactive ion etching. \emph{Journal of Vacuum Science and Technology A}, 12(4):1417-1424, July/August 1994.
	
	\bibitem{J.W. Coburn. Surface} J.W. Coburn. Surface-science aspects of plasma-assisted etching. \emph{Applied Physics A}, 59:451-458, November 1994.
	
	\bibitem{J.W. Coburn and M. Chen} J.W. Coburn and M. Chen. Optical emission spectroscopy of reactive plasmas: A method for correlating emission intensities to reactive particle density. \emph{Journal of Applied Physics}, 51(6);3134-3136, June 1980.
	
	\bibitem{J.W. Coburn and H.F. Winters} J.W. Coburn and H.F. Winters. Plasma etching - A discussion of mechanisms. \emph{Journal of Vacuum Science and Technology A}, 16(2):391-403, March/April 1979.
	
	\bibitem{T.J. Dalton} T.J. Dalton. \emph{Pattern Dependencies in the Plasma Etching of Polysilicon}. Ph.D. Dissertation, Massachusetts Institute of Technology, 1994.
	
	\bibitem{R.C. Dorf} R.C. Dorf. \emph{Modern Control Systems}. Addison-Wesley, 1989.
	
	\bibitem{J. C. Doyle and G. Stein} J. C. Doyle and G. Stein. Multivariable feedback design; Concepts for classical/modern synthesis. \emph{IEEE Transactions on Automatic Control}, 26(1):4-16, February 1981.
	
	\bibitem{D. Edelson and D.L. Flamm} D. Edelson and D.L. Flamm. Computer simulation of a CF4 plasma etching silicon. \emph{Journal of Applied Physics}, 56(5):1522-1531, September 1984.
	
	\bibitem{T.F. Edgar} T.F. Edgar. Model-based control of rapid thermal processes. \emph{In Extended Abstracts: 187th Meeting of the Electrochemical Society}, page 198, May 1995.
	
	\bibitem{M. Elta, H. Etemad} M. Elta, H. Etemad, J.S. Freudenberg, M.D. Giles, J.W. Grizzle, P.T. Kabamba, P.P. Khargonekar, S. Lafortune, S.M. Meerkov, J.R. Moyne, B.A. Rashap, D. Teneketzis, and F.L. Terry, Jr. Applications of real-time feedback control to semiconductor manufacturing; Reactive ion etching. \emph{In Proceedings of the 1993 American Controls Conference}, pages 2990-2995, June 1993.
	
	\bibitem{M. Elta, J. Fournier} M. Elta, J. Fournier, J.S. Freudenberg, M.D. Giles, J.W. Grizzle, P.T. Kabamba, P.P. Khargonekar, S. Lafortune, S.M. Meerkov, B.A. Rashap, F. L. Terry, Jr., and T. Vincent. Real-time feedback control of reactive ion etching. \emph{In Proceedings of the 1993 SPIE Symposium on Microelectronic Processing}, pages 438-451, September 1993.
	
	\bibitem{T.H. Fedynyshyn, G.W. Grynkewich}  T.H. Fedynyshyn, G.W. Grynkewich, and B.A. Chen T.P. Ma. The effect of metal masks on the plasma etch rate of sihcon. \emph{Journal of the Electrochemical Society}, 136(6);1799-1804, June 1989.
	
	\bibitem{T.H. Fedynyshyn, G.W. Grynkewick, and R.H. Dumas}  T.H. Fedynyshyn, G.W. Grynkewick, and R.H. Dumas. Mask dependent etch rates: III. the effect of a silver etch masking on the plasma etch rate of silicon. \emph{Journal of the Electrochemical Society}, 135(l);228-269, January 1988.
	
	\bibitem{T.H. Fedynyshyn, G.W. Grynkewick, T.B. Hook} T.H. Fedynyshyn, G.W. Grynkewick, T.B. Hook, M.D. Liu, and T.P. Ma. The effect of aluminum vs. photoresist masking on the etching rates of silicon and silicon dioxide in $\text{CF}_{4}/\text{O}_{2}$ plasmas. \emph{Journal of the Electrochemical Society}, 134(1):206-209, January 1987.
	
	\bibitem{citekey} T.H. Fedynyshyn, G.W. Grynkewick, and T.P. Ma. Mask dependent etch rates: II. The effect of aluminum vs. photoresist masking on the etching rates of silicon and silicon dioxide in $\text{CF}_{4}/\text{O}_{2}$ plasmas. \emph{Journal of the Electrochemical Society}, 134(10):2580-2585, October 1987.
	
	\bibitem{D.L. Flamm and Y.M. Donnelly}  D.L. Flamm and Y.M. Donnelly. The design of plasma etchants. \emph{Plasma Chemistry and Plasma Processing}, 1(4) :317-363, December 1981.
	
	\bibitem{J.P. Fournier, M.L. Passow} J.P. Fournier, M.L. Passow, T.J. Cotier, and M.E. Elta. A solution for pressure variations in vacuum process tools due to pressure regulator fluctuations. \emph{Journal of Vacuum Science and Technology A}, 9(2):358-359, March/April 1991.
	
	\bibitem{J.S. Freudenberg, J.W. Grizzle, and B.A. Rashap} J.S. Freudenberg, J.W. Grizzle, and B.A. Rashap. A feedback limitation of decentralized controllers for tito systems, with application to a reactive ion etcher. \emph{In Proceedings of the 33rd IEEE Conference on Decision and Control}, pages 2312-2317, December 1994.
	
	\bibitem{U. Gerlach-Meyer, J.W . Coburn} U. Gerlach-Meyer, J.W . Coburn, and E. Kay. Ion-enhanced gas-surface chemistry: the influence of the mass of the incident ion. \emph{Surface Science}, 103:177-188, 1981.
	
	\bibitem{R. Gottscho and V. Donnelly.} R. Gottscho and V. Donnelly. Optical emission actinometry and spectral line shapes in rf glow discharges. \emph{Journal of Applied Physics}, 56(2):245-250, July 1984.
	
	\bibitem{A. Grace, A.J. Laub, J.N. Little}  A. Grace, A.J. Laub, J.N. Little, and C.M. Thompson. \emph{Control System Toolbox: For Use with MATLAB}. The MathWorks, 1992.
	
	\bibitem{D.B. Graves. Plasma processing in microelectronics manufacturing.} D.B. Graves. Plasma processing in microelectronics manufacturing. \emph{AIChE Journal}, 35(l):l-29, January 1989.
	
	\bibitem{D.B. Graves. Plasma processing.} D.B. Graves. Plasma processing. \emph{IEEE Transactions on Plasma Science}, 22(l):31-42, February 1994.
	
	\bibitem{D.C. Gray, I. Tepermeister} D.C. Gray, I. Tepermeister, and H.H. Sawin. Phenomenological modeling of ionenhanced surface kinetics in fluorine-based plasma etching. \emph{Journal of Vacuum Science and Technology B}, 11(4):1243-1257, July/August 1993.
	
	\bibitem{A. Grill} A. Grill. \emph{Cold Plasma in Materials Fabrication: From Fundamentals to Applications}. IEEE Press, 1994.
	
	\bibitem{ D.S. Grimard.} D.S. Grimard. \emph{Utilizing Diffraction for Real-Time In Situ Wafer Monitoring}. Ph.D. Dissertation, University of Michigan, 1990.
	
	\bibitem{J.W. Grizzle, M.E. Elta} J.W. Grizzle, M.E. Elta, J.S. Freudenberg, P.P Khargonekar, and F.L. Terry, Jr. Improving rie process robustness via real-time feedback control. \emph{In Extended Abstracts: 187th Meeting of the Electrochemical Society}, pages 199-200, May 1995.
	
	\bibitem{P.D. Hanish, J.W. Grizzle,} P.D. Hanish, J.W. Grizzle, M.D. Giles, and F.L. Terry, Jr. A model-based technique for real-time estimation of absolute fluorine concentration in a $\text{CF}_{4}/\text{Ar}$ plasma. \emph{Journal of Vacuum Science and Technology A}, 13(3):1802-1807, M ay/June 1995.
	
	\bibitem{W.R. Harshbarger, R.A. Porter} W.R. Harshbarger, R.A. Porter, T.A. Miller, and P. Norton. A study of the optical emission from an rf plasma during semiconductor etching. \emph{Applied Spectroscopy}, 31(3):201-207, March 1977.
	
	\bibitem{O.S. Heavens} O.S. Heavens. \emph{Optical Properties of Thin Solid Films}. Dover Publications, 1965.
	
	\bibitem{E. Hecht} E. Hecht. \emph{Optics}. Addison-Wesley, 1987.
	
	\bibitem{J.S. Herman, T.E. Benson, O.D. Patterson} J.S. Herman, T.E. Benson, O.D. Patterson, C.Y. Chen, A.T. Demos, P.P. Khargonekar, F.L. Terry, Jr., and M.E. Elta. Real-time control of reactive ion etching of amorphous silicon for thin film transistor applications. \emph{In Proceedings of the 186th Meeting of the Electrochemical Society}, October 1994.
	
	\bibitem{N. Hershkowitz} N. Hershkowitz. How does the potential get from a to b in a plasma? \emph{IEEE Transactions on Plasma Science}, 22(1):11-21, February 1994.
	
	\bibitem{W. J. Hill and W. G. Hunter} W. J. Hill and W. G. Hunter. A review of response surface methodology: A literature survey. \emph{Technometrics}, 8(4):571-590, November 1966.
	
	\bibitem{R.A. Horn and C.R. Johnson} R.A. Horn and C.R. Johnson. \emph{Matrix Analysis}. Cambridge University Press, 1985.
	
	\bibitem{P. Horowitz and W. Hill} P. Horowitz and W. Hill. \emph{The Art of Electronics}. Cambridge University Press, 1989.
	
	\bibitem{I.H. Hutchinson} I.H. Hutchinson. \emph{Principles of Plasma Diagnostics}. Cambridge University Press, 1987.
	
	\bibitem{M.W. Jenkins, M.T. Mocella} M.W. Jenkins, M.T. Mocella, K.D. Allen, and H.H. Sawin. The modeling of plasma etching processes using response surface methodologies. \emph{Solid State Technology}, 29(4):175-182, April 1986.
	
	\bibitem{J. Jenq, J. Ding} J. Jenq, J. Ding, J.W. Taylor, and N. Hershkowitz. Absolute fluorine concentrations in RIE and ECR $\text{CF}_{4}$ plasmas measured by actinometry. \emph{Plasma Sources for Science and Technology}, 3:154-161, 1994.
	
	\bibitem{R.E. Jewett, P.I. Hagouel} R.E. Jewett, P.I. Hagouel, A.R. Neureuther, and T. van Duzer. Line-profile resist development simulation techniques. \emph{Polymer Engineering and Science}, 17(6):381-384, June 1977.
	
	\bibitem{T. Kailath} T. Kailath. \emph{Linear Systems}. Prentice-Hall, 1980.
	
	\bibitem{M. Kimizuka and K. Hirata} M. Kimizuka and K. Hirata. Pattern profile control of polysilicon etching. \emph{Journal of Vacuum Science and Technology B}, 3(1):16-19, January/February 1985.
	
	\bibitem{T.J. Knight, X. Cheng, D.W. Greve} T.J. Knight, X. Cheng, D.W. Greve, B.H. Krogh, and M.A. Gibson. Multivariable control of plasma enhanced chemical vapor deposition using real-time mass spectroscopy. \emph{In Proceeding of the Thirty-Second Annual Allerton Conference on Communication, Control, and Computing}, pages 765-773, September 1994,
	
	\bibitem{H.R. Koenig and L.I. Maissel} H.R. Koenig and L.I. Maissel. Application of rf discharges to sputtering. \emph{IBM Journal of research and development}, 14(2):168-171, March 1970.
	
	\bibitem{M.J. Kushner} M.J. Kushner. Monte-carlo simulation of electron properties in rf parallel plate capacitively coupled discharges. \emph{Journal of Applied Physics}, 54(9);4958-4965, September 1983.
	
	\bibitem{H.H. Lee} H.H. Lee. \emph{Fundamentals of Microelectronic Processing}. McGraw-Hill, 1990.
	
	\bibitem{Y.H. Lee and M. Chen} Y.H. Lee and M. Chen. Silicon etching mechanisms and anisotropy in $\text{CF}_{4}+\text{O}_{2}$ plasma. \emph{Journal of Applied Physics}, 54(10):5966-5973, October 1983.
	
	\bibitem{M.A. Lieberman and A.J. Lichtenberg} M.A. Lieberman and A.J. Lichtenberg. \emph{Principles of Plasma Discharges and Materials Processing}. John Wiley \& Sons, 1994.
	
	\bibitem{L. Ljung. System Identification Toolbox} L. Ljung. \emph{System Identification Toolbox: For Use with MATLAB}. The MathWorks, 1991.
	
	\bibitem{L. Ljung. System Identification} L. Ljung. \emph{System Identification: Theory for the User}. Prentice-Hall, 1987.
	
	\bibitem{D.P. Looze, F. Azad, B. Bernstein} D.P. Looze, F. Azad, B. Bernstein, and T. Collins. Control analysis and design for Czochralski growth of GaAs. \emph{In Proceeding of the Thirty-Second Annual Allerton Conference on Communication, Control, and Computing}, pages 794-803, September 1994.
	
	\bibitem{D.P. Looze, F. Azad, B. Bernstein, and T. Collins}  D.P. Looze, F. Azad, B. Bernstein, and T. Collins. Modeling and identification of the liquid encapsulated Czochralski GaAs process for control. \emph{Journal of Crystal Growth}, 148(l-2):79-95, 1995.
	
	\bibitem{D.M. Manos and D.L. Flamm} D.M. Manos and D.L. Flamm, editors. \emph{Plasma Etching}. Academic Press, 1989.
	
	\bibitem{The Mathworks} The Mathworks. \emph{Simulink User’s Guide}, 1993.
	
	\bibitem{J.L. Mauer, J.S. Logan, L.B. Zielinski} J.L. Mauer, J.S. Logan, L.B. Zielinski, and G.C. Schwartz. Mechanism of silicon etching by a CF4 plasma. \emph{Journal of Vacuum Science and Technology}, 15(5):1734- 1738, September/October 1978.
	
	\bibitem{K.J. McLaughlin} K.J. McLaughlin. \emph{Development of techniques for real-time monitoring and control in plasma etching}. Ph.D. Dissertation, University of Texas at Austin, 1989.
	
	\bibitem{K.J. McLaughlin, S.W. Butler} K.J. McLaughlin, S.W. Butler, T.F. Edgar, and I. Trachtenberg. Development of techniques for real-time monitoring and control in plasma etching: I. Response surface modeling of $\text{CF}_{4}/\text{O}_{2}$ and $\text{CF}_{4}/\text{H}_{2}$ etching of silicon and sihcon dioxide. \emph{Journal of the Electrochemical Society}, 138:789-799, March 1991.
	
	\bibitem{R.H. Middleton and G.C. Goodwin} R.H. Middleton and G.C. Goodwin. \emph{Digital Control and Estimation: A Unified Approach}. Prentice Hall, 1990.
	
	\bibitem{M.M Millard and E. Kay} M.M Millard and E. Kay. Difluorocarbene emission spectra from fluorocarbon plasmas and its relationship to fluorocarbon polymer formation. \emph{Journal of Electrochemical Society}, 129(1):160-165, January 1982.
	
	\bibitem{C.J. Mogab, A.C. Adams} C.J. Mogab, A.C. Adams, and D.L. Flamm. Plasma etching of Si and $\text{SiO}_{2}$ - The effect of oxygen additions to $\text{CF}_{4}$ plasma. \emph{J. Appl. Phys.}, 49(7):3796-3803, July 1978.
	
	\bibitem{T.M. Morris, D.S. Grimard} T.M. Morris, D.S. Grimard, C.S. Shu, F.L. Terry, Jr., M.E. Elta, and R.C. Jain. Utilizing diffraction imaging for non destructive wafer topography measurements. \emph{In Proceedings of the 1993 SP IE Symposium on Integrated Circuit Metrology, Inspection, and Process Control}, pages 27-32, March 1993
	
	\bibitem{M.R. Murnane, C.J. Raymond} M.R. Murnane, C.J. Raymond, S.L. Prins, S.S.H. Naqvi, and J.R. McNeil. Scatterometry for 0.24 firrt, - 0.70 p m developed photoresist metrology. \emph{In Proceedings of the 1995 SPIE Symposium on Integrated Circuit Metrology, Inspection, and Process Control}, pages 427-436, February 1995.
	
	\bibitem{N. Mutsukura, Y. Fukasawa} N. Mutsukura, Y. Fukasawa, Y. Machi, and T. Kubota. Diagnostics and control of radio-frequency discharge. \emph{Journal of Applied Physics}, 72:3126-3130, December 1994.
	
	\bibitem{National Research Council} National Research Council. \emph{Plasma Processing of Materials: Scientific Opportunities and Technology Challenges}, 1991.
	
	\bibitem{M.L. Passow} M.L. Passow. \emph{Microwave, R F and Hybrid Reactor Generated Discharges for Semiconductor Processing}. Ph.D. Dissertation, University of Michigan, 1991.
	
	\bibitem{L.C. Plumb and K.R. Ryan} L.C. Plumb and K.R. Ryan. A model of the chemical processes occuring in $\text{CF}_{4}/\text{O}_{2}$ discharges used in plasma etching. \emph{Plasma Chemistry and Plasma Processing}, 6(3):205-230, September 1986.
	
	\bibitem{B.A. Rashap, M. Elta} B.A. Rashap, M. Elta, H. Etemad, J.S. Freudenberg, J.P. Fournier, M.D. Giles, J.W. Grizzle, P.T. Kabamba, P.P. Khargonekar, S. Lafortune, J.R. Moyne, D. Teneketzis, and F.L. Terry, Jr. Control of semiconductor manufacturing equipment: Real-time feedback control of a reacHve ion etcher. \emph{IEEE Transactions on Semiconductor Manufacturing}, 8(3):286-297, August 1995.
	
	\bibitem{B.A. Rashap, J.S. Freudenberg} B.A. Rashap, J.S. Freudenberg, and M. Elta. Real-time feedback for sidewall profile control in reactive ion etching. \emph{Journal of Vacuum Science and Technology A}, 13(3):1792-1796, M ay/June 1995.
	
	\bibitem{citekey} B.A. Rashap, P.P. Khargonekar, M.E. Elta, J.S. Freudenberg, and F.L. Terry, Jr. Real-time control of reactive ion etching: Identification and disturbance rejection. \emph{In Proc. 1993 IEEE Conference on Decision and Control}, pages 3379-3385, December 1993.
	
	\bibitem{citekey} A.D. Richards, B.E. Thompson, K.D. Allen, and H.H. Sawin. Atomic chlorine concentration measurements in a plasma reactor. I. A comparison of infrared absorption and optical emission actinometry. Journal of Applied Physics, 3(1):792-807, August 1987.
	
	\bibitem{K.R. Ryan and I.C. Plumb. Kinetics} K.R. Ryan and I.C. Plumb. Kinetics of the reactions of CF3 with 0($^{3}$P) and O2 at 295k. \emph{The Journal of Physical Chemistry}, 86(24):4678-4683, 1982
	
	\bibitem{K.R. Ryan and I.C. Plumb. Gas} K.R. Ryan and I.C. Plumb. Gas-phase of the reactions of CF2 with 0($^{3}$P) to produce COF: Their significance in plasma processing. \emph{Plasma Chemistry and Plasma Processing}, 4(4):271-284, December 1984.
	
	\bibitem{K.R. Ryan and I.C. Plumb. A model} K.R. Ryan and I.C. Plumb. A model for the etching of Si in $\text{CF}_{4}$ plasmas; Comparison with experimental measurements. \emph{Plasma Chemistry and Plasma Processing}, 6(3):231-245, 1986.
	
	\bibitem{H.H. Sawin} H.H. Sawin. Challenges in dry etching: uniformity, selectivity, pattern dependencies, damage, and cleaning. \emph{Microelectronic Engineering}, 23:15-21, 1994.
	
	\bibitem{C. Schaper, Y. Cho} C. Schaper, Y. Cho, and T. Kailath. Low-order modeling and dynamic characterization of rapid thermal processing. \emph{Applied Physics A}, 54:317-326, April 1992.
	
	\bibitem{C. Schaper, M. Moslehi, K. Saraswat} C. Schaper, M. Moslehi, K. Saraswat, and T. Kailath. Control of MMST RTP: Repeatability, uniformity, and integration for flexible manufacturing. \emph{IEEE Transactions on Semiconductor Manufacturing}, 7(2):202-219, May 1994.
	
	\bibitem{C. Schaper, M. Moslehi} C. Schaper, M. Moslehi, K. Saraswat, and T. Kailath. Modeling, identification, and control of rapid thermal processing systems. \emph{Journal of the Electrochemical Society}, 141(ll):3200-3209, November 1994.
	
	\bibitem{Semiconductor Industry Association} Semiconductor Industry Association. \emph{The National Technology Roadmap for Semiconductors}, 1994.
	
	\bibitem{T. Soderstrom and P. Stoica} T. Soderstrom and P. Stoica. \emph{System Identification}. Prentice Hall, 1989
	
	\bibitem{M. Spak, D. Mammato} M. Spak, D. Mammato, S. Jain, and D. Durham. Mechanism and lithographic evaluation of image reversal in AZ 5214 photoresist. \emph{In Proceedings of the Seventh International Technical Conference on Photopolymers.}
	
	\bibitem{citekey} A.R. Striganov and N.S. Sventitskii. \emph{Tables of Spectral Lines of Neutral and Ionized Atoms}. IFI/Plenum, 1968.
	
	\bibitem{J.D. Stuber, I. Trachtenberg} J.D. Stuber, I. Trachtenberg, T.F. Edgar, J.K. Elliott, and T. Breedijk. Model-based control of rapid thermal processes. \emph{In Proceedings of the 33rd Conference on Decision and Control}, pages 79-85, December 1994.
	
	\bibitem{S.M. Sze} S.M. Sze, editor. \emph{VLSI Technology}. McGraw-Hill, 1983.
	
	\bibitem{C.M. Thompson and L Shure} C.M. Thompson and L Shure. \emph{Image Processing Toolbox: For Use with MATLAB}. The MathWorks, 1993.
	
	\bibitem{Y.Y. Tu, T.J. Chuang} Y.Y. Tu, T.J. Chuang, and H.F. Winters. Chemical sputtering of fluorinated silicon. \emph{Physical Review B}, 23(2):823-835, January 1981.
	
	\bibitem{T.L. Vincent, P.P. Khargonekar, and F.L. Terry} T.L. Vincent, P.P. Khargonekar, and F.L. Terry, Jr. A fast algorithm for real time etch rate measurement using single or multiple wavelength reflectometry. \emph{Submitted to 1995 Materials Research Society Fall Meeting}, 1995.
	
	\bibitem{T.L. Vincent, P.P. Khargonekar, B.A. Rashap} T.L. Vincent, P.P. Khargonekar, B.A. Rashap, F.L. Terry, Jr., and M.E. Elta. Nonlinear system identification and control of a reactive ion etcher. \emph{In Proceedings of the 1994 American Control Conference}, pages 902-905, 1994.
	
	\bibitem{H.F. Winters and J.W. Coburn} H.F. Winters and J.W. Coburn. Surface science aspects of etching reactions. \emph{Surface Science Reports}, 14(4-6);165-269, February 1992.
	
	\bibitem{S. Wolf} S. Wolf. \emph{Silicon Processing for the VLSI Era: Volume 2 - Process Integration}. Lattice Press, 1990.
	
	\bibitem{S. Wolf and R.N. Tauber} S. Wolf and R.N. Tauber. \emph{Silicon Processing for the VLSI Era: Volume 1 - Process Technology}. Lattice Press, 1986.
	
	\bibitem{M.J. Zucrow} M.J. Zucrow. \emph{Gas Dynamics}. John Wiley \& Sons, 1976.
	
\end{thebibliography}